\chapter{Results}%
\label{ch:results}
In this chapter the results of the \VHbb\ multi-variate discriminant fit are
shown. Other results such as those for the cross-checks of the analysis can be
found in~\cite{VHMainNote2019}. The fit is performed in accordance with the
asymptotic approximation~\cite{Cowan:2010js} for calculating the $p_0$ values,
which are converted to statistical significances expressed in terms of standard
deviations. An Asimov dataset conditional on $\mu=1$  is generated for use in
the above approximation and is used in a fit whose nuisance parameter pulls are
compared with those coming from the unconditional fit to the data that is used
to generate the final results. As per the prescription of the asymptotic
approximation the results will be discussed in the context of a hypothesis test
comparing the null hypothesis, the background only model, with the alternative
hypothesis, the background plus signal model.

My contributions to the results are as already stated in other chapters plus
running the combined, and 2--lepton channel fits to generate and study the
results at many key milestones in the publication timeline including the final
results in the paper~\cite{final-paper}.

\section{Nuisance Parameter Pulls}
Figure~\ref{fig:nppulls_012L_MVAVH_a} shows the nuisance parameter pulls coming
from the combined profile-likelihood fit for the $W+$jets, $Z+$jets and top
process backgrounds.
\input{08-results/pullcomp}
The other nuisance parameter pulls have been omitted but have been
studied~\cite{VHMainNote2019}, and the \texttt{Sys} has been dropped from the
names of the parameters displayed. Observation of the pull on \texttt{SysZMbb}
shows that it is pulled towards the $+1\sigma$ value which meets the
expectations based on the shapes derived in section~\ref{sec:zjets-shapes}. The
uncorrelated component of the shape, which is pulled in that direction but to a
lesser degree this also matches expectations. Several of the nuisance parameters
relating to the BDTr shape uncertainties are pulled to either $+1\sigma$ or
$-1\sigma$ as would be expected, whilst several have not been pulled much which
goes against naive expectations. There could be many explanations for this but
as the phase space is split up into many different regions limiting the
statistical power of the method it is best not to over-interpret. In order to
understand the behaviour of the uncertainties, the correlations between nuisance
parameter pulls, shown in figure~\ref{fig:np-corrs}, must be studied.
\input{08-results/np-corrs}
There are no correlations which indicate an unexpected relationship between the
relevant quantities.

\section{Breakdown and Ranking of Uncertainties}
Table~\ref{tab:breakdown_012L_MVAVH} shows a breakdown of the impact of the
systematic uncertainties on the signal strength measurement.
\input{08-results/comb-breakdown}
It can be seen that the total statistical uncertainty (DataStat) has a smaller
impact than the uncertainties due to modelling and experimental sources
(FullSyst). Considering the systematic uncertainties, those coming from
experimental sources have a greater impact than those coming from the modelling
of the signal, which in turn have a greater impact than those coming from the
modelling of the background. Further scrutiny of uncertainties on the signal
strength comes in the form of the ranking shown in
figures~\ref{fig:Rank_012L_MVAVH} and~\ref{fig:Rank_012L_MVAVH_nosig}.
\input{08-results/ranking}
The rankings are determined by change in $\mu$ resulting from shifting a given
nuisance parameter. The nuisance parameter in question is moved to its up and
down variation, based on post-fit uncertainty, represented by the blue boxes
that are empty and hatched respectively. The variations based on the pre-fit
uncertainty are represented by the yellow area.

It can be seen that the ranking is dominated by uncertainties on the signal. The
post-fit ranking which omits signal uncertainties is largely dominated by
flavour tagging uncertainties and scale factors for normalisation and acceptance
between analysis regions. The highest ranked uncertainty in both cases is the
$b$-tagging efficiency. This is unsurprising as $b$-tagging plays a crucial role
in the analysis selection. Notably the $Z+$jets shape uncertainties do not
appear in the top sources of uncertainty. Naively this is unexpected as the
background dominates in a sensitive channel of the analysis, however, other
modelling uncertainties which are described with multi-variate techniques have a
greater impact.

\section{Post-fit Data Versus Predictions}
Figures~\ref{fig:0lep2jet-postfit}, \ref{fig:0lep3jet-postfit},
\ref{fig:1lep2jet-postfit}, \ref{fig:1lep3jet-postfit},
\ref{fig:2lep2jet-postfit}, \ref{fig:2lep3pjet-postfit} show the post-fit data
versus prediction comparisons for each of the analysis channel and jet
multiplicity combinations. Each figure shows the individual analysis regions
based on $\Delta R(b, b)$ region and $p_{\mathrm{T}}^V$ bin. Across the board
good agreement between the data and prediction can be seen, supporting the
conclusion that our uncertainty model covers all of the differences between the
two datasets and the supporting the background plus signal hypothesis.
\input{08-results/0lep-2jet-postfit}
\input{08-results/0lep-3jet-postfit}
\input{08-results/1lep-2jet-postfit}
\input{08-results/1lep-3jet-postfit}
\input{08-results/2lep-2jet-postfit}
\input{08-results/2lep-3pjet-postfit}

\clearpage

\section{Signal Strength and STXS Measurements}
In this section the signal strength and STXS measurements will be detailed.

\subsection{\VH\ Signal Strength Measurement}
Table~\ref{tab:sig_channels} shows the expected and observed significances for
the background plus signal hypothesis broken down by analysis channel.
\input{08-results/channel-sig}
The expected significances were determined using an Asimov dataset conditional
on $\mu=1$. All channels are approaching the 5$\sigma$ threshold to claim
discovery and the combined fit is well above the discovery threshold, in
agreement with the previous result~\cite{vhbb-obs}. Figure~\ref{fig:channel-mus}
shows the best fit values for the signal strength in each channel and in the
combined paradigm.
\input{08-results/channel-mus}
All measurements are compatible with the standard model prediction of $\mu=1$.
The composition and values of the uncertainties affecting each channel are
similar with the 2--lepton channel being slightly more impacted by statistical
rather than systematic uncertainty. The measurement of \VH signal strength is
also compatible with the CMS Collaboration result of $1.01 \pm
0.22$~\cite{CMS:hbb}, corresponding measurements of the \WH and \ZH processes as
well as the cross-section have not yet been published. 
% \input{08-results/uncorrelated-mus}
\clearpage
\subsection{\WH\ and \ZH\ Signal Strength Measurements}
Table~\ref{tab:sig_WZH} shows the expected and observed significances for
the background plus signal hypothesis for the \WH\, \ZH\ and \VH measurements.
\input{08-results/WH-ZH-sig}
The expected significances were determined using an Asimov dataset conditional
on $\mu=1$. The \WH\ stand alone measurement is approaching the 5$\sigma$
threshold to claim discovery. The \ZH\ stand alone measurement has surpassed the
threshold and the paper associated with this measurement is first proof of
discovery~\cite{final-paper}. Figure~\ref{fig:WZH-mus} shows the best fit values
for the signal strength for each measurement.
\input{08-results/WH-ZH-mus}
All measurements are compatible with the standard model prediction of $\mu=1$,
the composition and values of the uncertainties affecting each channel are very
similar.
\clearpage

\subsection{Simplified Template Cross-section Measurements}
Table~\ref{tab:sig_stxs} shows the expected and observed significances for
the \VHbb\ cross-section measurement in the each STXS bin. All bins have an
observed statistical significance in line with what was expected.
Figure~\ref{fig:5POI-mus} shows the best fit values for the cross-section times
branching ratio ($\sigma \times B$) in each of the STXS bins.
\input{08-results/stxs-sig}
All measurements are compatible with the standard model predictions and are
weakly limited by statistical uncertainty. The theoretical uncertainty on the
standard  model prediction is greater for \ZH\ bins than for \WH\ bins.
\input{08-results/stxs-mus}
Figure~\ref{fig:5POI-corr} shows the correlation between each STXS bin. It can
be seen that no two bins are strongly correlated with one another. The lack of
correlation is largely due to the analysis categorisations which serve as
independent measurements of each STXS bin.
\input{08-results/stxs-corrs}
%\input{08-results/stxs-results-table}
%\input{08-results/stxs-fancy}
